Kepler and the Behemoth: Three Mini-Neptunes in a 40 Million Year Old Association

### 2022-04-30 papers/ms.tex
update ms

% 208 words (250 max)
\begin{abstract}
  %The best way to measure a planet's age is to ignore the planet and
  %pay attention to the star.
  Stellar positions and velocities from Gaia are yielding a new window
  on open cluster dispersal.  
  Here we present an analysis of a group
  of stars spanning Cepheus ($l=100^\circ$) to Hercules ($l=40^\circ$),
  hereafter the Cep-Her complex.  The group includes four Kepler
  Objects of Interest:
  Kepler-1643 b ($R_{\rm p} = 2.32 \pm 0.14\,R_\oplus$, $P = 5.3\ {\rm days}$),
  KOI-7368 b ($R_{\rm p} = 2.22 \pm 0.12\,R_\oplus$, $P = 6.8\ {\rm days}$), 
  KOI-7913 Ab ($R_{\rm p} = 2.34 \pm 0.18\,R_\oplus$, $P = 24.2\ {\rm days}$), and
  Kepler-1627 Ab ($R_{\rm p} = 3.85 \pm 0.11\,R_\oplus$, $P = 7.2\ {\rm days}$).
  The latter Neptune-sized planet is in part of the Cep-Her complex
  called the $\delta$\ Lyr\ cluster \citep{bouma_kep1627_2022}.  Here
  we focus on the former three systems, which are in other regions of
  the association.  Based on kinematic evidence from Gaia, stellar
  rotation periods from TESS, and spectroscopy, these three objects
  are also $\approx$40 million years (Myr) old.  More specifically, we
  find that Kepler-1643 is $46^{+9}_{-7}$\,Myr old, based on its
  membership in a dense sub-cluster of the complex called RSG-5.
  KOI-7368 and KOI-7913 are $36^{+10}_{-8}$\,Myr old, and are in a
  diffuse region that we call CH-2.  Based on the transit shapes and
  high resolution imaging, all three objects are most likely planets,
  with false positive probabilities of $6\times10^{-9}$,
  $4\times10^{-3}$, and $1\times10^{-4}$ for Kepler-1643, KOI-7368,
  and KOI-7913 respectively.  These planets demonstrate
  that mini-Neptunes with sizes of $\sim$2 Earth radii exist at ages
  of 40 million years.
\end{abstract}

@@

The prime Kepler mission \citep{borucki_kepler_2010} found most of the
currently known transiting exoplanets, and it was conducted before
Gaia.  It is therefore sensible to revisit the Kepler field, given our
new knowledge of the stellar ages.

@@

		\vspace{-0.6cm}
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f2c.pdf}
			\includegraphics[width=0.49\textwidth]{f2d.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf The stellar groups near KOI-7368, KOI-7913, and Kepler-1643
    are 40 to 50 million years old.} 
    {\it Top row}: Color--absolute magnitude diagram of candidate
    Cep-Her members, plotted over candidate members of the
    $\delta$~Lyr~cluster ($\approx38$\,Myr;
    \citealt{bouma_kep1627_2022}) and the Gaia EDR3 Catalog of Nearby
    Stars (gray background).  The left and right columns shows stars
    in RSG-5 and CH-2, respectively.  The range of colors is truncated
    to emphasize the pre-main-sequence.  Stars that fall far below the
    cluster sequences are field interlopers.  {\it Bottom row}: TESS
    and ZTF-derived stellar rotation periods, with the Pleiades
    ($\approx 112$\,Myr) and Praesepe ($\approx 650$\,Myr) shown for
    reference \citep{rebull_rotation_2016a,douglas_poking_2017}.  The
    detection efficiency for reliable rotation periods falls off
    beyond $\bpmrpo \gtrsim 2.6$.
	\label{fig:age}
	}
\end{figure*}

@@

Color--absolute magnitude diagrams (CAMDs) of the candidate RSG-5 and
CH-2 members are shown in the upper row of Figure~\ref{fig:age}.  The
stars from the $\delta$~Lyr cluster are from
\citet{bouma_kep1627_2022}, and the field stars are from the Gaia EDR3
Catalog of Nearby Stars \citep{gaia_gcns_2021}.  To make these
diagrams, we imposed the data filtering criteria from
\citet[][Appendix B]{GaiaCollaboration2018}, which include binaries
while omitting artifacts from for instance low
photometric signal to noise, or a small number of visibility periods.
We then corrected for extinction using the
\citet{lallement_threedimensional_2018} dust
maps and the extinction
coefficients $k_X\equiv A_X/A_0$ from \citet{GaiaCollaboration2018},
assuming that $A_0 = 3.1 E(B-V)$.  This yielded a mean and standard
deviation for the reddening of $E(B-V)=0.036\pm0.002$ for RSG-5, and
$E(B-V)=0.017\pm0.001$ for CH-2.  By way of comparison, in
\citet{bouma_kep1627_2022} the same query for the $\delta$~Lyr cluster
yielded $E(B-V)=0.032\pm0.006$.  Finally, for the plots we set the
color range to best visualize the region of maximal age information
content: the pre-main-sequence.

@@

From a data-driven perspective, demonstrating that a group of stars
was physically associated at its time of formation is challenging.
While some young groups show kinematic evidence for expansion
\citep{kuhn_kinematics_2019}, many, including Sco-Cen, do not
\citep{wright_kinematics_2018}.  This complicates the feasibility of
deriving kinematic ages through traceback, as well as through the
expansion itself \citep[see][]{crundall_chronostar_2019}.  A more
minimal approach is that suggested by \citet{tofflemire_2021}: search
for coeval, phase-space neighbors, measure their ages, and determine
if they share a common age.  This approach can demonstrate whether a
star is currently associated with a set of coeval stars, though it
falls short of determining what the association looked like in the
past.  While our analysis of CH-2 meets the latter standard for
demonstrating the
existence of a $\approx$40\,Myr stellar association, it does not meet
the standard of demonstrating that its stars were associated at birth. 
It would be a worthy exercise for future work to perform a similar
search for coeval phase-space neighbors on the entire dataset of known
exoplanet hosts.  For the time being, we can offer the anecdotal point
that in our experience, most stars do not have dozens of 40\,Myr
neighbors within a local volume of a few \kms\ and tens of parsecs.

@@

\facilities{
 	{\it Astrometry}:
 	Gaia \citep{gaia_collaboration_gaia_2018,gaia_collaboration_2021_edr3}.
 	{\it Imaging}:
    Second Generation Digitized Sky Survey. %,
    %SOAR~(HRCam; \citealt{tokovinin_ten_2018}).
 	Keck:II~(NIRC2; \url{www2.keck.hawaii.edu/inst/nirc2}).
 	%Gemini:South~(Zorro; \citealt{scott_nessi_2018}.
 	%Gemini:North~(`Alopeke; \citealt{scott_nessi_2018,scott_twin_2021}.
 	{\it Spectroscopy}:
	%CTIO1.5$\,$m~(CHIRON; \citealt{tokovinin_chironfiber_2013}),
  %PFS ({\bf CITE}),
	Tillinghast:1.5m~(TRES; \citealt{furesz_tres_2008}).
  %MPG2.2$\,$m~(FEROS; \citealt{kaufer_commissioning_1999}),
	%AAT~(Veloce; \citealt{gilbert_veloce_2018}).
	%AAT~(HERMES; \citealt{lewis_2002_hermers_2df,sheinis_2015_hermes}),
 	Keck:I~(HIRES; \citealt{vogt_hires_1994}).
 	%VLT:Kueyen~(FLAMES; \citealt{pasquini_2002}).
% 	Euler1.2m~(CORALIE),
% 	ESO:3.6m~(HARPS; \citealt{mayor_setting_2003}).
 	{\it Photometry}:
%	  ASTEP:0.40$\,$m (ASTEP400),
% 	CTIO:1.0m (Y4KCam),
% 	Danish 1.54m Telescope,
%	  El Sauce:0.356$\,$m,
% 	Elizabeth 1.0m at SAAO,
% 	Euler1.2m (EulerCam),
	  Kepler \citep{borucki_kepler_2010},
% 	Magellan:Baade (MagIC),
% 	Max Planck:2.2m	(GROND; \citealt{greiner_grond7-channel_2008})
%   MuSCAT3 \citep{Narita_2020},
% 	NTT,
% 	SOAR (SOI),
 	  TESS \citep{ricker_transiting_2015},
% 	TRAPPIST \citep{jehin_trappist_2011},
% 	VLT:Antu (FORS2).
    ZTF \citep{bellm_zwicky_2019}.
}

@@

\paragraph{Table~2} contains 338 candidate Cep-Her members with weights
$D>0.02$ observed by Kepler.  The final catalog of candidate
Cep-Her members will be provided by R.~Kerr et al.\ in prep; Table~2 is
from a preliminary version of that work.  Note that more
restrictive weight cuts should be imposed if one wishes to remove
the majority of field star interlopers.
Table~2 was created by cross-matching candidate Cep-Her members
(selected using Gaia EDR3; Section~\ref{subsec:members}) against a
Kepler to Gaia DR2 cross-match (the \texttt{gaia-kepler.fun}
crossmatch database created by Megan Bedell).  The
\texttt{kic\_dr2\_ang\_dist} column is from the latter table.  The
EDR3 to DR2 match was performed using the
\texttt{gaiaedr3.dr2\_neighbourhood} table, and the closest proper
motion and epoch-corrected angular distance neighbor was taken as the
single best match.  The \texttt{edr3\_dr2\_mag\_diff} column gives
some indication of the reliability of this EDR3 to DR2 conversion, as
there are a few cases between Gaia DR2 and EDR3 where partially
resolved binaries became fully resolved.

>>>>

% 208 words (250 max)
\begin{abstract}
  %The best way to measure a planet's age is to ignore the planet and
  %pay attention to the star.
  Stellar positions and velocities from Gaia are yielding a new view
  of open cluster dispersal.  
  Here we present an analysis of a group
  of stars spanning Cepheus ($l=100^\circ$) to Hercules ($l=40^\circ$),
  hereafter the Cep-Her complex.  The group includes four Kepler
  Objects of Interest:
  Kepler-1643 b ($R_{\rm p} = 2.32 \pm 0.14\,R_\oplus$, $P = 5.3\ {\rm days}$),
  KOI-7368 b ($R_{\rm p} = 2.22 \pm 0.12\,R_\oplus$, $P = 6.8\ {\rm days}$), 
  KOI-7913 Ab ($R_{\rm p} = 2.34 \pm 0.18\,R_\oplus$, $P = 24.2\ {\rm days}$), and
  Kepler-1627 Ab ($R_{\rm p} = 3.85 \pm 0.11\,R_\oplus$, $P = 7.2\ {\rm days}$).
  The latter Neptune-sized planet is in part of the Cep-Her complex
  called the $\delta$\ Lyr\ cluster \citep{bouma_kep1627_2022}.  Here
  we focus on the former three systems, which are in other regions of
  the association.  Based on kinematic evidence from Gaia, stellar
  rotation periods from TESS, and spectroscopy, these three objects
  are also $\approx$40 million years (Myr) old.  More specifically, we
  find that Kepler-1643 is $46^{+9}_{-7}$\,Myr old, based on its
  membership in a dense sub-cluster of the complex called RSG-5.
  KOI-7368 and KOI-7913 are $36^{+10}_{-8}$\,Myr old, and are in a
  diffuse region that we call CH-2.  Based on the transit shapes and
  high resolution imaging, all three objects are most likely planets,
  with false positive probabilities of $6\times10^{-9}$,
  $4\times10^{-3}$, and $1\times10^{-4}$ for Kepler-1643, KOI-7368,
  and KOI-7913 respectively.  These planets demonstrate
  that mini-Neptunes with sizes of $\sim$2 Earth radii exist at ages
  of 40 million years.
\end{abstract}

@@

The prime Kepler mission \citep{borucki_kepler_2010} found most of the
currently known transiting exoplanets, and it was conducted before
Gaia.  It is therefore sensible to revisit the Kepler field, given our
new constraints on the stellar ages.

@@

		\vspace{-0.6cm}
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f2c.pdf}
			\includegraphics[width=0.49\textwidth]{f2d.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Age-diagnostic diagrams from the stellar groups near
    Kepler-1643, KOI-7368, and KOI-7913.} 
    {\it Top row}: Color--absolute magnitude diagram of candidate
    Cep-Her members, plotted over candidate members of the
    $\delta$~Lyr~cluster ($\approx38$\,Myr;
    \citealt{bouma_kep1627_2022}) and the Gaia EDR3 Catalog of Nearby
    Stars (gray background).  The left and right columns shows stars
    in RSG-5 and CH-2, respectively.  The range of colors is truncated
    to emphasize the pre-main-sequence.  Stars that fall far below the
    cluster sequences are field interlopers.  {\it Bottom row}:
    TESS and ZTF-derived stellar rotation periods, with the Pleiades
    ($\approx 112$\,Myr) and Praesepe ($\approx 650$\,Myr) shown for
    reference \citep{rebull_rotation_2016a,douglas_poking_2017}.  The
    detection efficiency for reliable rotation periods falls off
    beyond $\bpmrpo \gtrsim 2.6$.
	\label{fig:age}
	}
\end{figure*}

@@

Color--absolute magnitude diagrams (CAMDs) of the candidate RSG-5 and
CH-2 members are shown in the upper row of Figure~\ref{fig:age}.  The
stars from the $\delta$~Lyr cluster are from
\citet{bouma_kep1627_2022}, and the field stars are from the Gaia EDR3
Catalog of Nearby Stars \citep{gaia_gcns_2021}.  To make these
diagrams, we imposed the data filtering criteria from
\citet{GaiaCollaboration2018}, which include binaries
while omitting artifacts from for instance low
photometric signal to noise, or a small number of visibility periods.
We then corrected for extinction using the
\citet{lallement_threedimensional_2018} dust
maps and the extinction
coefficients $k_X\equiv A_X/A_0$ from \citet{GaiaCollaboration2018},
assuming that $A_0 = 3.1 E(B-V)$.  This yielded a mean and standard
deviation for the reddening of $E(B-V)=0.036\pm0.002$ for RSG-5, and
$E(B-V)=0.017\pm0.001$ for CH-2.  By way of comparison, in
\citet{bouma_kep1627_2022} the same query for the $\delta$~Lyr cluster
yielded $E(B-V)=0.032\pm0.006$.  Finally, for the plots we set the
color range to best visualize the region of maximal age information
content: the pre-main-sequence.

@@

From a data-driven perspective, demonstrating that a group of stars
was physically associated at its time of formation is challenging.
While some young groups show kinematic evidence for expansion
\citep{kuhn_kinematics_2019}, many, including Sco-Cen, do not
\citep{wright_kinematics_2018}.  This complicates the feasibility of
deriving kinematic ages through traceback, as well as through the
expansion itself \citep[see][]{crundall_chronostar_2019}.  A more
minimal approach is that suggested by \citet{tofflemire_2021}: search
for coeval, phase-space neighbors, measure their ages, and determine
if they share a common age.  This approach can demonstrate whether a
star is currently associated with a set of coeval stars, though it
falls short of determining what the association looked like in the
past.  Our analysis of CH-2 meets the latter standard for
demonstrating the
existence of a $\approx$40\,Myr stellar association.

It would be a worthy exercise for future work to perform a similar
search for coeval phase-space neighbors on the entire dataset of known
exoplanet hosts.  For the time being, we can offer the anecdotal point
that in our experience, most stars do not have dozens of 40\,Myr
neighbors within a local volume of a few \!\kms\ and tens of parsecs.

@@

\facilities{
 	{\it Astrometry}:
 	Gaia. % \citep{gaia_collaboration_gaia_2018,gaia_collaboration_2021_edr3}.
 	{\it Imaging}:
    Second Generation Digitized Sky Survey. %,
    %SOAR~(HRCam; \citealt{tokovinin_ten_2018}).
 	Keck:II~(NIRC2).
 	%Gemini:South~(Zorro; \citealt{scott_nessi_2018}.
 	%Gemini:North~(`Alopeke; \citealt{scott_nessi_2018,scott_twin_2021}.
 	{\it Spectroscopy}:
	%CTIO1.5$\,$m~(CHIRON; \citealt{tokovinin_chironfiber_2013}),
  %PFS ({\bf CITE}),
	Tillinghast:1.5m~(TRES).
  %MPG2.2$\,$m~(FEROS; \citealt{kaufer_commissioning_1999}),
	%AAT~(Veloce; \citealt{gilbert_veloce_2018}).
	%AAT~(HERMES; \citealt{lewis_2002_hermers_2df,sheinis_2015_hermes}),
 	Keck:I~(HIRES).
 	%VLT:Kueyen~(FLAMES; \citealt{pasquini_2002}).
% 	Euler1.2m~(CORALIE),
% 	ESO:3.6m~(HARPS; \citealt{mayor_setting_2003}).
 	{\it Photometry}:
%	  ASTEP:0.40$\,$m (ASTEP400),
% 	CTIO:1.0m (Y4KCam),
% 	Danish 1.54m Telescope,
%	  El Sauce:0.356$\,$m,
% 	Elizabeth 1.0m at SAAO,
% 	Euler1.2m (EulerCam),
	  Kepler,
% 	Magellan:Baade (MagIC),
% 	Max Planck:2.2m	(GROND; \citealt{greiner_grond7-channel_2008})
%   MuSCAT3 \citep{Narita_2020},
% 	NTT,
% 	SOAR (SOI),
 	  TESS,
% 	TRAPPIST \citep{jehin_trappist_2011},
% 	VLT:Antu (FORS2).
    ZTF.
}

@@

\paragraph{Table~2} contains 338 candidate Cep-Her members with weights
$D>0.02$ observed by Kepler.  The complete catalog of candidate
Cep-Her members will be provided by R.~Kerr et al.\ in prep.\ using Gaia DR3; Table~2 is
from an early version of that analysis based on Gaia EDR3.  Note that more
restrictive weight cuts should be imposed if one wishes to remove
the majority of field star interlopers.
Table~2 was created by cross-matching candidate Cep-Her members
(selected using Gaia EDR3; Section~\ref{subsec:members}) against a
Kepler to Gaia DR2 cross-match (the \texttt{gaia-kepler.fun}
crossmatch database created by Megan Bedell).  The
\texttt{kic\_dr2\_ang\_dist} column is from the latter table.  The
EDR3 to DR2 match was performed using the
\texttt{gaiaedr3.dr2\_neighbourhood} table, and the closest proper
motion and epoch-corrected angular distance neighbor was taken as the
single best match.  The \texttt{edr3\_dr2\_mag\_diff} column gives
some indication of the reliability of this EDR3 to DR2 conversion, as
there are a few cases between Gaia DR2 and EDR3 where partially
resolved binaries became fully resolved.
